\textsc{Atomic modeling of argon}\\ \footnotesize{\textsc{Project 5 --- FYS3150}}

### 2015-11-30 projects/project_5/molecular_dynamics/article/article.tex
fixed a reference
fixed src indentation
blabla

    Of interest now is how our new method of integration compares with the old
    one. One way of looking at this is by examining the fluctuations in the
    total energy as functions of the time step $\Delta t$. This will be
    examined in upcoming sections.

@@

    In order to compute the \emph{mean square displacement} in section
    \ref{sub:melting_temperature_of_system} we need to keep track of the
    initial position of each atom. We therefore introduce a variable
    \texttt{m\_initialPosition} in the \texttt{Atom-class} which is set during
    initialization.  When computing the diffusion constant $D$, we need to make
    sure that $r_i^2(t)$ is the true displacement, and not the displacement
    relative to the nearest periodic image. This will be implemented in the
    \texttt{applyBoundaryConditions}-method.

@@

In order to measure the melting temperature of the system, we can use the Einstein relation which states the following:
\begin{equation}
    \notag
    \langle r^2(t) \rangle = 6Dt.
\end{equation}
$D$ is here the diffusion constant, $t$ is time and the \emph{mean square displacement} is calculated as
\begin{equation}
    \notag
    r_i^2(t) = \left| \vec{r}_i(t) - \vec{r}_i(0) \right|^2
\end{equation}
for atom $i$.

>>>>

    Of interest now is how our new method of integration compares with the old
    one. One way of looking at this is by examining the fluctuations in the
    total energy as functions of the time step $\Delta t$. This will be
    examined in section \ref{sub:energy_conservation_of_integration_method}.

@@

    In order to compute the \emph{mean square displacement} in section
    \ref{sub:melting_temperature_of_system} we need to keep track of the
    initial position of each atom. We therefore introduce a variable
    \texttt{m\_initialPosition} in the \texttt{Atom-class} which is set during
    initialization.  When computing the diffusion constant $D$, we need to make
    sure that $r_i^2(t)$ is the true displacement, and not the displacement
    relative to the nearest periodic image. This will be implemented in the
    \texttt{applyBoundaryConditions}-method and is as simple as in addition to
    moving the position of the atom, also move the initial position of the atom
    by the same amount, because then the relative distance between instantaneous
    position and initial position is equal to the true displacement.

@@

    In order to measure the melting temperature of the system, we can use the
    Einstein relation which states the following:
    \begin{equation}
        \notag
        \langle r^2(t) \rangle = 6Dt.
    \end{equation}
    $D$ is here the diffusion constant, $t$ is time and the \emph{mean square
    displacement} is calculated as
    \begin{equation}
        \notag
        r_i^2(t) = \left| \vec{r}_i(t) - \vec{r}_i(0) \right|^2
    \end{equation}
    for atom $i$. Solving this for $D$ gives yields
    \begin{equation}
        \notag
        D = \frac{\langle r^2(t) \rangle}{6t}.
    \end{equation}
    We can now make set of simulations for varying initial temperature $T$.
